Towards Verifying the Bitcoin-S Library

### 2019-07-03 paper/paper.tex
changes to paper

What will turn out to be more relevant are the Scala features which
Stainless does not support, such as: (concrete) class definitions,
inheritance by objects, abstract type members, and inner classes in
case objects.

Also, Stainless has its own library of some core data types and
functions which need to be mapped correctly to functions inside of the
SMT solver that Stainless ultimately relies on. Those data types in
general do not have all the methods of the Scala data types. For
example, the BigInt type in Scala has a methods for bitwise operations
while the BigInt type in Stainless does not.

@@

@@

The addition will now look like this:
\begin{lstlisting}[style=scala]
  def +(c: CurrencyUnit): CurrencyUnit = {
    Satoshis(satoshis.underlying + c.satoshis.underlying)
  } ensuring(res =>
    (c.satoshis == Satoshis.zero) ==>
      (res.satoshis == this.satoshis))
\end{lstlisting}

>>>>

What will turn out to be more relevant for us are the Scala features
which Stainless does not support, such as: (concrete) class
definitions, inheritance by objects, abstract type members, and inner
classes in case objects.

Also, Stainless has its own library of some core data types and
functions which need to be mapped correctly to functions inside of the
SMT solver that Stainless ultimately relies on. Those data types in
general do not have all the methods of the Scala data types. For
example, the BigInt type in Scala has methods for bitwise operations
while the BigInt type in Stainless does not.

@@

why fix the preconditions:
\begin{itemize}
\item all green: new errors stand out more
\item at runtime, errors are caught earlier, which is preferrable
\end{itemize}

@@

The addition will now look like this:
\lstinputlisting[style=scala, firstline=15, lastline=18, firstnumber=15]{../code/addition/src/main/scala/verified/currency/CurrencyUnits.scala}
